**Statistical Inference Course Project**
#
*author: sbstolk (January 24 2015)*
#
**Overview**
#
The goal of this simulation is to compare the sampling of expotential distributions simulated in R with the results predicted by the Central Limit Theorem. 
An exponential distribution is simulated in R using the code rexp(n, lambda) where lambda is the rate parameter. For this simuation, lambda is set equal to 0.2.
The distribution of averages of 40 expotentials are examined via 1000 simulatied distributions. 
#
**Simulation**
#
The theoretical mean of this distribution is calculated as 1/lambda. For lambda = 0.2, the theoretical mean is 5. 
This will be compared to the outcome of the simulation. The simulations were created using a function as follows.
```{r}
expdist <- rep(NA,1000)
for (i in 1:1000){
     expdist[i] <- mean(rexp(40,0.2))
}
```

**Results**
The mean of the simulations was calculated. 
```{r}
> expMean <-mean(expdist)
> expMean
#[1] 5.008841
```
This is only 0.0088 larger (1.8% larger) than the calculated theoretical mean of 5.
It can be said that the difference is statistically negligible and that the theoretical calculation is correct. 
#
The theoretical variance is ((1/lambda)^2)/n, which is ((1/0.2)^2)/40 for the simulation model. The expected theoretical variance is 0.625
The variance of the simulations was calculated. 
```{r}
> expVar <-var(expdist)
> expVar
#[1] 0.6498142
```
The result is within 4% of the expected variance, from which it can be said that the theoretical estimate is correct. 


