

**Synopsis**
The analysis was conduted on the results of a study comparing tooth length in guinea pigs to the relative dose of Vitamin C. 60 guinea pigs were included in the study.
10 guinea pigs each were randomly assigned to one of 6 groups.  Each group was associated with a dose level of Vitamin C (0.5mg, 1mg and 2 mg) and a delivery method (orange juice or ascorbic acid).
The analysis will indicate if there is any statisticaly significant difference in tooth growth between groups. 

**Analysis**
First, the data was loaded in R. 
```{r}
library(datasets)
data(ToothGrowth)
```
To get an overview of the result, the data was plotted in *ggplot2*. 
```{r}
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
  geom_bar(stat="identity",)
  facet_grid(. ~ supp)
  xlab("Dose in mg")
  ylab("Tooth length")
  guides(fill=guide_legend(title="Tooth Growth by Supplement Type"))
```
The plot shows a strong positive correlation between increased Vitamin C dosage and increased tooth growth. However, it is less obvious if there is an effect from delivery method. 
This can be examined by running independent linear models of the relationship between each variable and tooth length.

```{r}
fit <- lm(len ~ supp, data=ToothGrowth)
summary(fit)
```
From these results, we can see that the suppliment type explains 5.95% of the variation in tooth growth. 

```{r}
fit2 <-lm(len~dose,data=ToothGrowth)
 summary(fit2)
 ```
 This shows that 64.4% of variation in tooth growth is attributible to the doseage of Vitamin C. 
 The process is repeated to check for a combined effect of dose and suppliment type. 
```{r} 
toothfit <- lm(len~dose+supp, data = ToothGrowth)
summary(toothfit)
```
In total, 70.4% of variation in guinea pig tooth growth in this experiment can be attributed to a combination of the Vitamin C dosage and delivery method. 
To check the significance of these results

```{r}
confint(toothfit)
```
The result shows that the null hypothesis (ie, that Vitamin C dosage and delivery has no effect on guniea pig tooth growth) can be rejected in this instance. 
